---
title: "Crosstalk"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{crosstalk}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Crosstalk allows two data visuals to 'talk' to one another. To use {crosstalk} in {echarts4r}, add `selectedMode`. Crosstalk can be used in Markdown and Quarto to add interaction like one would see in Shiny.

WORKS: NULL, cartesian2d, m

Not supported for Web GL and 3-D charts. coord_system = calendar, polar, geo, geo3D, globe etc.
As of writing this (March-2026) crosstalk seems to be broken in {leaflet}.

Crosstalk is supported for the following chart types:
-   `e_area()`
-   `e_bar()`
-   `e_candle()`
-   `e_density()`
-   `e_effect_scatter()`
-   `e_funnel()`
-   `e_heatmap()`
-   `e_histogram()`
-   `e_line()`
-   `e_pictorial()`
-   `e_pie()`
-   `e_scatter()`
-   `e_step()`

Crosstalk works with timeline and grouped data. Working with grouped data, the keys have to be set to the group.


```{r setup}
library(echarts4r)
library(crosstalk)
library(DT)

sd <- SharedData$new(mtcars |> tibble::rownames_to_column("model"))

bscols(
  sd |>
    e_charts(model) |>
    e_bar_("mpg",     selectedMode = "single",
           emphasis = list(
             focus='self', blurScope='series'
           ),
           blur = list(
             itemStyle = list(
               opacity = 0.3
             ))) |> e_brush(),
  datatable(sd)
)
```

```{r}
sd <- USArrests |> tibble::rownames_to_column("State") |> SharedData$new()

bscols(
  sd |>
    e_charts(State) |>
    e_scatter(Murder, name = "Start", step = "start", fill = TRUE, selectedMode = 'single',
           blur = list(
             itemStyle = list(
               opacity = 0.3          # dim non-selected bars strongly
             ))),
    sd |>
    e_charts(State) |>
    e_bar(Murder, name = "Start", step = "start", fill = TRUE, selectedMode = 'single',
           blur = list(
             itemStyle = list(
               opacity = 0.3          # dim non-selected bars strongly
             ))),
  datatable(sd, extensions="Scroller", style="bootstrap", class="compact", width="100%",
            options=list(deferRender=TRUE, scrollY=300, scroller=TRUE))
)
```



