---
title: "Crosstalk"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{crosstalk}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

{crosstalk} allows for interactive filtering of data across multiple widgets without requiring a Shiny server. Crosstalk integration in {echarts4r} enables linked brushing and filtering between echarts charts and other crosstalk-compatible widgets such as DT tables and Leaflet maps.

Crosstalk can be used in Markdown and Quarto to add interaction like one would see in Shiny.

Crosstalk is supported for the following chart types:

-   `e_area()`
-   `e_bar()`
-   `e_candle()`
-   `e_density()`
-   `e_effect_scatter()`
-   `e_funnel()`
-   `e_heatmap()`
-   `e_histogram()`
-   `e_line()`
-   `e_pictorial()`
-   `e_pie()`
-   `e_scatter()`
-   `e_step()`

Of these chart types, cartesian2d and no coordinate system are supported while timeline is also supported. Data requiring crosstalk functionality must be used in `e_charts().` Functions that add data to an echart (such as `e_add()`) is not supported. 

This integration has not been tested in Shiny.

## How it Works

Charts are linked via a shared SharedData object.

will highlight or filter in response to selections made in other widgets, and selections made on an echarts chart — via click or brush — will propagate to linked widgets.


## Example
To use {crosstalk} in {echarts4r}, add `selectedMode` argument. This can be `TRUE` or one of  `single`, `multiple` or `series`. 

```{r setup}
library(echarts4r)
library(crosstalk)
library(dplyr)
library(DT)
library(htmltools)

sd <- SharedData$new(mtcars |> tibble::rownames_to_column("model"))

# Yes, it's a linked object
crosstalk::is.SharedData(sd)

bscols(
  sd |>
    e_charts(model) |>
    e_bar_("mpg",     selectedMode = TRUE),
  datatable(sd, class="compact", width="100%")
)
```

Let's add more style to make highlight more obvious. Much better!

```{r}
bscols(
  sd |>
    e_charts(model) |>
    e_bar_("mpg", selectedMode = "single",
           emphasis = list(
             focus='self'
           ),
           blur = list(
             itemStyle = list(
               opacity = 0.3
             ))) |> e_brush(),
  datatable(sd, class="compact", width="100%")
)
```



## With Grouped Data

Grouping data must be done before a SharedData object is created. Furthermore, `key` argument must be used - `key` must be a unique id.

```{r}
# This data set, each row represents a vehicle name, so can be used as a key
sdf <- mtcars |>
  group_by(cyl) |>
  SharedData$new(key = ~rownames(mtcars))

p <- sdf |> e_charts(hp) |> e_line(mpg,
    selectedMode = 'multiple',
    select = list(itemStyle= list(color='magenta')),
    emphasis = list(focus='self', blurScope='series'),
    blur= list(itemStyle= list(opacity = 0.3))
  )

styl <- 'width:50%;display:block;float:left;'
bscols(
  list(
    filter_slider("hp", "Horsepower", sdf, ~hp, width = "100%"),
    div(style=styl, filter_checkbox("cyl", "Cylinders", sdf, ~cyl, inline=TRUE)),
    div(style=styl, filter_checkbox("gear", "Gears", sdf, ~gear, inline=TRUE)),
    filter_select("carb", "Carburetors (select)", sdf, ~carb),
    datatable(sdf,
              class="compact", width="100%", height=350,
              extensions="Scroller", style="bootstrap",
              options=list(scroller=TRUE, deferRender=TRUE, scrollY=200)
    )
  ),
  list(p)
)
```


## Crosstalk with Two Charts

When two charts are using crosstalk, selected point(s) are highlighted and non-selected points are downplayed.

```{r}
sd <- USArrests |> tibble::rownames_to_column("State") |> SharedData$new()

bscols(
  sd |>
    e_charts(State) |>
    e_scatter(Murder, selectedMode = 'multiple',
                     emphasis = list(
             focus='self'
           ),
           blur = list(
             itemStyle = list(
               opacity = 0.3 
             ))),
    sd |>
    e_charts(State) |>
    e_bar(Murder, selectedMode = 'single',
            emphasis = list(
             focus='self'
           ),
           blur = list(
             itemStyle = list(
               opacity = 0.3
             ))),
  datatable(sd, class="compact", width="100%")
)
```

## Timeline
```{r}
grouped_sd <- iris |>
  distinct(Species, .keep_all = TRUE) |> 
  dplyr::group_by(Species) |>
  SharedData$new(key = ~Species)

bscols(
  grouped_sd |> e_chart(Species, timeline = TRUE) |>
  e_bar_("Sepal.Length", selectedMode = "single",            blur = list(
    itemStyle = list(
      opacity = 0.3
    ))
  ),
  grouped_sd |> e_chart(Species, timeline = TRUE) |>
  e_bar_("Sepal.Length", selectedMode = "single",            blur = list(
    itemStyle = list(
      opacity = 0.3
    ))
  ),
  datatable(grouped_sd, extensions="Scroller", style="bootstrap", class="compact", width="100%",
            options=list(deferRender=TRUE, scrollY=300, scroller=TRUE))
)

```




